\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-10-30 parts-infer-param.tex
switch from interval parameters to integer parameters (minus the running example)

\modLP{
Hence, we propose in \pref{ssec:admissible-K} the notion of \emph{compatible} parametrization with respect
ot the PH dynamics: a Thomas model is compatible with a PH if Thomas dynamics is included in the PH
dynamics, i.e., all the transitions in the Thomas model are possible transitions in the PH.
This relaxed notion of parameterization compatibility allows to enumerate all parametrizations
compatible with a given PH, i.e. all Thomas model whose dynamics is included in the PH dynamics.}

@@

\todo{update notations}
\begin{property}[Parameter validity]\label{pro:K-valid}
A parameter $K_{a,\omega}$ is valid w.r.t. the PH if and only if the following equation is verified:
\begin{align*}
  \forall a_i\in C^a_{a,\omega}, a_i \notin K_{a,\omega} \Longrightarrow
    (& \exists \PHfrappe{c_k}{a_i}{a_j}\in\PHa, c_k \in C^c_{a,\omega} \\
     & \wedge a_i < K_{a,\omega} \Rightarrow j > i \wedge  a_i > K_{a,\omega} \Rightarrow j <i )
\end{align*}
\end{property}

@@

\begin{property}[Extreme values assumption]
Let $\IG = (\Gamma, E)$ be an IG. A parametrization $K$ on $\IG$ satisfies the \emph{extreme values assumption} if and only if:
\label{pro:param_enum_extreme}
\begin{align*}
  \forall b \in \Gamma, \GRNreg{b} \neq \emptyset \Longrightarrow \exists \omega \subset \GRNreg{b}, 0 \in K_{b,\omega} \wedge \exists \omega' \subset \GRNreg{b}, l_b \in K_{b,\omega'}
\end{align*}
\end{property}

@@

\begin{property}[Monotonicity assumption]
\label{pro:param_enum_monotonicity}
Let $\IG = (\Gamma, E)$ be an IG. A parametrization $K$ on $\IG$ satisfies the \emph{monotonicity assumption} if and only if:
\begin{align*}
  \forall b \in \Gamma,
  \forall A^+ \subset \{ a \in \Gamma \mid \GRNedge{a}{+}{t}{b} \in E_+ \}&,
  \forall A^- \subset \{ a \in \Gamma \mid \GRNedge{a}{-}{t}{b} \in E_- \},\\
  K_{b,\omega \cup A^-} & \leqsegm K_{b,\omega \cup A^+}
\end{align*}
\end{property}

@@

Finally, we note that $\segm{1}{1}$ belongs to the possible values for both parameters.
Therefore this enumeration allows, from the model in \pref{fig:runningPH-1},
to find the behavior of the model refined with a cooperative sort described in \pref{fig:runningPH-2}.
\end{example}

>>>>

\modLP{
Hence, we propose in \pref{ssec:admissible-K} the notion of \emph{compatible} parametrization with respect
ot the PH dynamics: a Thomas model is compatible with a PH if Thomas dynamics is included in the PH
dynamics, i.e., all the transitions in the Thomas model are possible transitions in the PH.
This relaxed notion of parameterization compatibility allows to enumerate all parametrizations
compatible with a given PH, \ie all Thomas model whose dynamics is included in the PH dynamics.}

@@

\begin{property}[Parameter validity]\label{pro:K-valid}
A parameter $K_{a,\omega}$ is valid w.r.t.~the PH if and only if the following equation is verified:
\begin{align*}
  \forall a_i \in C^a_{a,\omega}, a_i \neq K_{a,\omega} \Longrightarrow
    (& \exists \PHfrappe{c_k}{a_i}{a_j}\in\PHa, c_k \in C^c_{a,\omega} \\
     & \wedge a_i < K_{a,\omega} \Rightarrow j > i \wedge  a_i > K_{a,\omega} \Rightarrow j <i )
\end{align*}
\end{property}

@@

\begin{property}[Extreme values assumption]
Let $\IG = (\Gamma, E)$ be an IG. A parametrization $K$ on $\IG$ satisfies the \emph{extreme values assumption} if and only if:
\label{pro:param_enum_extreme}
\begin{align*}
  \forall b \in \Gamma, \GRNreg{b} \neq \emptyset \Longrightarrow
    \exists \omega \subset \GRNreg{b}, K_{b,\omega} = 0 \wedge
    \exists \omega' \subset \GRNreg{b}, K_{b,\omega'} = l_b
\end{align*}
\end{property}

@@

\begin{property}[Monotonicity assumption]
\label{pro:param_enum_monotonicity}
Let $\IG = (\Gamma, E)$ be an IG. A parametrization $K$ on $\IG$ satisfies the \emph{monotonicity assumption} if and only if:
\begin{align*}
  \forall b \in \Gamma,
  \forall A^+ \subset \{ a \in \Gamma \mid \GRNedge{a}{+}{t}{b} \in E_+ \}&,
  \forall A^- \subset \{ a \in \Gamma \mid \GRNedge{a}{-}{t}{b} \in E_- \},\\
  K_{b,\omega \cup A^-} & \leq K_{b,\omega \cup A^+}
\end{align*}
\end{property}

@@

Finally, we note that $\segm{1}{1}$ belongs to the possible values for both parameters.
Therefore this enumeration allows, from the model in \pref{fig:runningPH-1},
to find the behavior of the model refined with a cooperative sort described in \pref{fig:runningPH-2}.
\todo{Refresh this example with integer parameters}
\end{example}
